\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-06 chapters/1_intro.tex
Update images and reduce sizes

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
\caption{
\TODO{Intro image caption} % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

>>>>

\begin{figure}[t]
\centering
% \includegraphics[width=0.5\textwidth,trim=0.4in 1.2in 0.in 0.05in,clip]{./figs/intro_image.jpg} % left bottom right top
\includegraphics[width=\textwidth]{./figs/intro_image.pdf} % left bottom right top
\caption{
{\small (\textbf{a}) Some iterations of the generalized algorithm on toy graphs with attractive (green) and repulsive (red) interactions. (\textbf{b}) Example of CREMI 2016 data \cite{cremiChallenge} overlaid with instance segmentation. (\textbf{c}) Agglomeration order, representing which pairs of neighboring pixels were merged first (blue) and later on (red).
We note how similar update rules, like \emph{Sum} (in the middle) and \emph{Mean} (on the right), lead to strongly different merging orders. 
% On the left: a single cluster is returned with only attractive interactions.
}
 % main ideas and contributions
\label{fig:intro_figure}}
\end{figure}

### 2019-05-06 chapters/2_rel_work.tex
Update images and reduce sizes

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for joint segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrent}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

>>>>

\textbf{Proposal-free methods} adopt a bottom-up approach by directly grouping pixels into instances. For example, the approach proposed in \cite{kirillov2017instancecut} uses a combinatorial framework for joint segmentation; SGN \cite{liu2017sgn} sequentially group pixels into lines and then instances;
% encode instance relationships to classes and exploit the boundary information  \cite{jin2016object}; 
a watershed transform is learned in \cite{bai2017deep} by also predicting its gradient direction, whereas the template matching \cite{uhrig2016pixel} deploys scene depth information.
Others use metric learning to predict high-dimensional associative pixel embeddings that map pixels of the same instance close to each other, while mapping pixels belonging to different instances further apart \cite{fathi2017semantic,newell2017associative,de2017semantic,kulikov2018instance}. % Semi-convolutiona: \cite{novotny2018semi}
% \TODO{What about \cite{liang2018proposal} using spectral clustering?}. 
Final instances are then retrieved by applying a clustering algorithm, like in the end-to-end trainable mean-shift pipeline of \cite{kong2018recurrentPix}.
%  and introducing a ﬁxed number of labels (colors) and then dynamically assigning object instances to those labels during training (coloring) \cite{kulikov2018instance}

### 2019-05-06 chapters/3_algorithm.tex
Update images and reduce sizes

@@

\begin{minipage}{\textwidth}
        \centering
        \begin{minipage}{0.49\textwidth}
\centering
        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
\captionof{figure}{ 
Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (red bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}. 
\label{fig:edge_contraction_and_contr_graph}  }
    \end{minipage}\hspace{0.01\textwidth}
    \begin{minipage}{0.49\textwidth}
        \centering
\includegraphics[width=\textwidth,trim=0.in 0.in 0.in 0.in,clip]{./figs/add_constraints.pdf}
\captionof{figure}{ 
\UPDATE{Comparison of \algname{}  with (top) and without (bottom) enforcing cannot-link constraints on a toy graph with positive (green) and repulsive (red) interactions. Only contracted graph is represented; every column represent one iteration of the algorithm; the selected edge at each iteration is highlighted in yellow; constrained edges are represented with red bars. We note that the two resulting clusterings are different.}
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{minipage}

@@

\begin{table*}
    \centering
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{r l || c | c | c}
            % \toprule\toprule
             & &  \multirow{3}{*}{\textbf{Unsigned graphs}}  & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            & & &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\

            & & &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hierarchical Aggl.\\Clustering} & \thead{Greedy Additive \\ Edge Contraction \\\cite{keuper2015efficient}} & \thead{Greedy \\Fixation \\\cite{levinkov2017comparative}} \\ \midrule

            \makecell[r]{Abs. \\ max:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} & \thead{Mutex \\Watershed \\\cite{wolf2018mutex}} \\ \midrule
            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hierarchical Clust. \\(UPGMA) \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl. Clust. \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hierarchical Aggl.\\Clustering \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl. Clust. \\ (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hierarchical Aggl.\\Clustering \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl. Clust. \\ (\textbf{NEW})} & \thead{\textbf{NEW}}

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{The table lists the tested update rules $f$. Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}
    \label{tab:linkage-criteria}
\end{table*}

>>>>

\begin{figure}
        \centering
        \begin{minipage}{0.49\textwidth}
\centering
        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
\captionof{figure}{ 
{\small Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}. }
\label{fig:edge_contraction_and_contr_graph}  }
    \end{minipage}\hspace{0.01\textwidth}
    \begin{minipage}{0.49\textwidth}
        \centering
\includegraphics[width=0.91\textwidth]{./figs/add_constraints.pdf}
\captionof{figure}{ 
{\small Some iterations of the generalized algorithm  with (top) and without (bottom) adding cannot-link constraints. The graph has both attractive (green) and repulsive (red) edges; cannot-link constraints are given by violet bars. At each iteration, the edge selected by the algorithm is highlighted in yellow. When cannot-link constraints are enforced, the final clustering is given by two clusters instead of only one.}
\label{fig:algorithm_with_without_CLC}}
    \end{minipage}
\end{figure}

@@

@@

\begin{table*}
    \centering
    \scriptsize
    \begin{subtable}[t!]{\textwidth}\centering
        \begin{tabular}{r  l || c | c | c}
            % \toprule\toprule
            \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
             &  &  &  \thead{\textsc{No}} & \thead{\textsc{Yes}} \\        
            % \cmidrule[0.3em]{3-5}
            % \midrule[0.15em]
            \midrule\midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} & \thead{Sum Linkage\\Hier. Aggl. Clust.} & \thead{Greedy Additive \\ Edge Contraction \cite{keuper2015efficient}} & \thead{Greedy Fixation\\\cite{levinkov2017comparative}} \\ \midrule

            \makecell[r]{Absolute \\Max:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Mutex Watershed \\\cite{wolf2018mutex}} & \thead{Mutex Watershed\\\cite{wolf2018mutex}} \\ \midrule
            \makecell[r]{Mean:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                                 & \thead{ Average Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Average Linkage\\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Max: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Single Linkage\\Hier. Aggl. Clust. \cite{lance1967general}} & \thead{Single Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}\\ \midrule

            Min:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $}                                 & \thead{Complete Linkage\\ Hier. Aggl. Clust. \cite{lance1967general}}  & \thead{Complete Linkage \\Signed Aggl. Clust. (\textbf{NEW})} & \thead{\textbf{NEW}}

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{{\small The table lists the tested update rules $f$. Existing and new algorithms are given by a specific choice of update rule, type of graph (signed or unsigned) and optional use of cannot-link constraints.}}
    \label{tab:linkage-criteria}
\end{table*}

### 2019-05-06 chapters/5_experiments_noise.tex
Update images and reduce sizes

\begin{figure}
\centering
        \begin{subfigure}[t]{0.48 \textwidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=0.35in 0.35in 0.35in 0.35in,clip]{./figs/merge_noise.pdf}

        \caption{Merge-biased opensimplex noise} \label{fig:thresh}
    \end{subfigure}%
    \begin{subfigure}[t]{0.48 \textwidth}
        \centering
        \includegraphics[width=0.98\textwidth,trim=0.29in 0.31in 0.31in 0.31in,clip]{./figs/split_noise.pdf}
        \caption{Split-biased opensimplex noise} \label{fig:ws}
    \end{subfigure}

\caption{Plot of the Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights. Solid lines represent median values, whereas values between the 25th and the 75th percentile are shown in shade areas.}\label{fig:noise_plots}
\end{figure}

>>>>

\begin{figure}
\centering
        \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise.pdf}

        \caption{Merge-biased noise added to edge weights} \label{fig:thresh}
    \end{subfigure}%
    \begin{subfigure}[t]{0.49 \textwidth}
        \centering
        \includegraphics[width=\textwidth,trim=0.53in 0.35in 0.65in 0.80in,clip]{./figs/split_noise.pdf}
        \caption{Split-biased noise added to edge weights} \label{fig:ws}
    \end{subfigure}

\caption{{\small Rand-Scores achieved by the generalized algorithm and different update rules when noise is added to the edge weights. Solid lines represent median values; values between the 25th and the 75th percentile are shown in shade areas. In the plots at the top, long-range connections are not used.}}\label{fig:noise_plots}
\end{figure}
